---
title: "Anxiety Meta-Analysis"
author: "Maria Schweer-Collins"
date: "`r Sys.Date()`"
output: html_document

        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install pacman if needed
#install.packages('pacman')

pacman::p_load(tidyverse, readxl, robumeta, metafor, rio, here)

## adding in TOST function for meta-analysis from this source: 
## https://osf.io/uvy8n (Original code shown below from OSF)
## https://doi.org/10.1177/1948550617697177 (Article)

#' @title TOST function for meta-analysis
#' @description
#'
#' `r lifecycle::badge('stable')`
#'
#' A function for providing TOST tests of equivalence from meta-analysis results.
#'
#' @param ES meta-analytic effect size
#' @param var meta-analytic variance
#' @param se standard error
#' @param low_eqbound_d lower equivalence bounds (e.g., -0.5) expressed in standardized mean difference (Cohen's d)
#' @param high_eqbound_d upper equivalence bounds (e.g., 0.5) expressed in standardized mean difference (Cohen's d)
#' @param alpha alpha level (default = 0.05)
#' @param plot set whether results should be plotted (plot = TRUE) or not (plot = FALSE) - defaults to TRUE
#' @param verbose logical variable indicating whether text output should be generated (verbose = TRUE) or not (verbose = FALSE) - default to TRUE
#' @return Returns TOST Z-value 1, TOST p-value 1, TOST Z-value 2, TOST p-value 2,  alpha, low equivalence bound d, high equivalence bound d, Lower limit confidence interval TOST, Upper limit confidence interval TOST
#' 
#' 
TOSTmeta<-function(ES,var,se,low_eqbound_d, high_eqbound_d, alpha, plot = TRUE, verbose = TRUE){
  if(missing(alpha)) {
    alpha<-0.05
  }

  if(missing(var)) {
    if(missing(se)) {
      stop("Need to specify variance (var) or standard error (se).")
    }
  }
  if(missing(se)) {
    se<-sqrt(var)
  }
  if(low_eqbound_d >= high_eqbound_d) warning("The lower bound is equal to or larger than the upper bound. Check the plot and output to see if the bounds are specified as you intended.")
  if(1 <= alpha | alpha <= 0) stop("The alpha level should be a positive value between 0 and 1.")
  Z1<-(ES-low_eqbound_d)/se
  p1<-pnorm(Z1, lower.tail=FALSE)
  Z2<-(ES-high_eqbound_d)/se
  p2<-pnorm(Z2, lower.tail=TRUE)
  Z<-(ES/se)
  pttest<-2*pnorm(-abs(Z))
  LL90<-ES-qnorm(1-alpha)*(se)
  UL90<-ES+qnorm(1-alpha)*(se)
  LL95<-ES-qnorm(1-alpha/2)*(se)
  UL95<-ES+qnorm(1-alpha/2)*(se)
  ptost<-max(p1,p2) #Get highest p-value for summary TOST result
  Ztost<-ifelse(abs(Z1) < abs(Z2), Z1, Z2) #Get lowest t-value for summary TOST result
  results<-data.frame(Z1,p1,Z2,p2,LL90,UL90)
  colnames(results) <- c("Z-value 1","p-value 1","Z-value 2","p-value 2", paste("Lower Limit ",100*(1-alpha*2),"% CI",sep=""),paste("Upper Limit ",100*(1-alpha*2),"% CI",sep=""))
  testoutcome<-ifelse(pttest<alpha,"significant","non-significant")
  TOSToutcome<-ifelse(ptost<alpha,"significant","non-significant")

  # Plot results
  if (plot == TRUE) {
  plot(NA, ylim=c(0,1), xlim=c(min(LL95,low_eqbound_d,ES)-max(UL95-LL95, high_eqbound_d-low_eqbound_d,ES)/10, max(UL95,high_eqbound_d,ES)+max(UL95-LL95, high_eqbound_d-low_eqbound_d, ES)/10), bty="l", yaxt="n", ylab="",xlab="Effect size")
  points(x=ES, y=0.5, pch=15, cex=2)
  abline(v=high_eqbound_d, lty=2)
  abline(v=low_eqbound_d, lty=2)
  abline(v=0, lty=2, col="grey")
  segments(LL90,0.5,UL90,0.5, lwd=3)
  segments(LL95,0.5,UL95,0.5, lwd=1)
  title(main=paste("Equivalence bounds ",round(low_eqbound_d,digits=3)," and ",round(high_eqbound_d,digits=3),"\nEffect size = ",round(ES,digits=3)," \n TOST: ", 100*(1-alpha*2),"% CI [",round(LL90,digits=3),";",round(UL90,digits=3),"] ", TOSToutcome," \n NHST: ", 100*(1-alpha),"% CI [",round(LL95,digits=3),";",round(UL95,digits=3),"] ", testoutcome,sep=""), cex.main=1)
  }


  if(missing(verbose)) {
    verbose <- TRUE
  }
  if(verbose == TRUE){
    cat("TOST results:\n")
    cat("Z-value lower bound:",format(Z1, digits = 3, nsmall = 2, scientific = FALSE),"\tp-value lower bound:",format(p1, digits = 1, nsmall = 3, scientific = FALSE))
    cat("\n")
    cat("Z-value upper bound:",format(Z2, digits = 3, nsmall = 2, scientific = FALSE),"\tp-value upper bound:",format(p2, digits = 1, nsmall = 3, scientific = FALSE))
    cat("\n\n")
    cat("Equivalence bounds (Cohen's d):")
    cat("\n")
    cat("low eqbound:", paste0(round(low_eqbound_d, digits = 4)),"\nhigh eqbound:",paste0(round(high_eqbound_d, digits = 4)))
    cat("\n\n")
    cat("TOST confidence interval:")
    cat("\n")
    cat("lower bound ",100*(1-alpha*2),"% CI: ", paste0(round(LL90, digits = 3)),"\nupper bound ",100*(1-alpha*2),"% CI:  ",paste0(round(UL90,digits = 3)), sep = "")
    cat("\n\n")
    cat("NHST confidence interval:")
    cat("\n")
    cat("lower bound ",100*(1-alpha),"% CI: ", paste0(round(LL95, digits = 3)),"\nupper bound ",100*(1-alpha),"% CI:  ",paste0(round(UL95,digits = 3)), sep = "")
    cat("\n\n")
    cat("Equivalence Test Result:\n")
    message(cat("The equivalence test was ",TOSToutcome,", Z = ",format(Ztost, digits = 3, nsmall = 3, scientific = FALSE),", p = ",format(ptost, digits = 3, nsmall = 3, scientific = FALSE),", given equivalence bounds of ",format(low_eqbound_d, digits = 3, nsmall = 3, scientific = FALSE)," and ",format(high_eqbound_d, digits = 3, nsmall = 3, scientific = FALSE)," and an alpha of ",alpha,".",sep=""))
    cat("\n")
    cat("Null Hypothesis Test Result:\n")
    message(cat("The null hypothesis test was ",testoutcome,", Z = ",format(Z, digits = 3, nsmall = 3, scientific = FALSE),", p = ",format(pttest, digits = 3, nsmall = 3, scientific = FALSE),", given an alpha of ",alpha,".",sep=""))
    if(pttest <= alpha && ptost <= alpha){
      combined_outcome <- paste0("NHST: reject null significance hypothesis that the effect is equal to ", 0," \n",
                                 "TOST: reject null equivalence hypothesis")
    }
    if(pttest < alpha && ptost > alpha){
      combined_outcome <- paste0("NHST: reject null significance hypothesis that the effect is equal to ",0," \n",
                                 "TOST: don't reject null equivalence hypothesis")
    }
    if(pttest > alpha && ptost <= alpha){
      combined_outcome <- paste0("NHST: don't reject null significance hypothesis that the effect is equal to ",0," \n",
                                 "TOST: reject null equivalence hypothesis")
    }
    if(pttest > alpha && ptost > alpha){
      combined_outcome <-  paste0("NHST: don't reject null significance hypothesis that the effect is equal to ",0," \n",
                                  "TOST: don't reject null equivalence hypothesis")
    }
    cat("\n")
    message(combined_outcome)
  }
  # Return results in list()
  invisible(list(ES=ES,TOST_Z1=Z1,TOST_p1=p1,TOST_Z2=Z2,TOST_p2=p2,alpha=alpha,low_eqbound_d=low_eqbound_d,high_eqbound_d=high_eqbound_d, LL_CI_TOST=LL90,UL_CI_TOST=UL90,LL_CI_ZTEST=LL95,UL_CI_ZTEST=UL95,NHST_t = t, NHST_p = pttest))
}

#' 
#' @examples
## Run TOSTmeta by specifying the standard error
## Anxiety Symptoms
## TOSTmeta(ES=0.09, se=0.0372, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)
## Depression Symptoms
TOSTmeta(ES=0.07, se=0.0257, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)
## Well-Being
TOSTmeta(ES=0.06, se=0.0626, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)
#' ## Run TOSTmeta by specifying the variance
#' TOSTmeta(ES=0.12, var=0.0081, low_eqbound_d=-0.2, high_eqbound_d=0.2, alpha=0.05)
#' ## If both variance and se are specified, TOSTmeta will use standard error and ignore variance
#' TOSTmeta(ES=0.12, var=9999, se = 0.09, low_eqbound_d=-0.2, high_eqbound_d=0.2, alpha=0.05)
#' @section References:
#' Rogers, J. L., Howard, K. I., & Vessey, J. T. (1993). Using significance tests to evaluate equivalence between two experimental groups. Psychological Bulletin, 113(3), 553, formula page 557.
#' @export
#'



```

## Import

Import meta-analysis data from merge script

```{r import}

d_anxiety <- import(here("data", "Anxiety_Symptoms.xlsx"))
d_depression <- import(here("data", "Depression_Symptoms.xlsx"))
d_wellbeing <- import(here("data", "Well_being.xlsx"))
d_adiagnosis <- import(here("data", "Anxiety_diagnosis.xlsx"))
## no other outcomes imported added to analysis due to insufficient K/n
## All data (outcomes) will be imported to the descriptive analysis script and merged

## Filter the intervention vs. active comparison to remove per Sean's input (drops two rows in both datsets)
# removing one row for depression focused intervention (moves to merge script)

d_anxiety <- d_anxiety %>%
  filter(refid != 10062) %>%
  filter(effect_intervention_group != "2-Thiswayup Schools: Combating Depression")

# 118 obs
# k = 28

d_anxiety_pubY <- d_anxiety %>%
  filter(public_m == "yes")


d_depression <- d_depression %>%
  filter(refid != 10062) %>%
  filter(effect_intervention_group != "2-Thiswayup Schools: Combating Depression")

# 53 obs
# K = 17

d_wellbeing <- d_wellbeing%>%
  filter(refid != 10062)

# 15 obs
# K unsure due to non-independence

d_adiagnosis

# 8 observations trimmed due to non-independence
# k = 8
```

## Meta-Analysis Code

The code below is for reporting the meta-analysis results in the report. 

Only anxiety and depression symptoms have adequate DF for RVE
Only well-being and anxiety diagnoses outcomes have enough K for regular meta-analysis

Models are run using metafor, and in most cases,
multivariate metafor models with RVE using `robust` function in metafor

### KQ1a: What is the effect of school based anxiety prevention interventions on anxiety symptoms?

#### Anxiety Symptoms

Meta-analysis results: 
  
```{r MA-anxiety-symptoms, width = 10, tidy = TRUE}

# MODEL 1 RVE ##########################################


## make decision about RCADS for Refid 10064 (all mutually exclusive so retain)


# create effect size id variable 'esid'
d_anxiety <- d_anxiety %>%
  group_by(refid) %>%
  mutate(esid = row_number())

# construct var-cov matrix assuming a correlation of 0.8 for effect sizes corresponding to the same study using vcalc function

as_V2 <- vcalc(via, cluster = refid,  obs=esid, data = d_anxiety, rho=0.8)

# Specify comparison model: metafor multilevel random-effects model with effect sizes nested within study 

# sigma is between study heterogeneity and within study heterogeneity
as_metafor <- rma.mv(yi, as_V2, random = ~1| refid/esid,  data = d_anxiety)
as_metafor


## obtain prediction interval 
print(predict(as_metafor))

# applying robust variance estimation
# data clustered by study
# adjust = TRUE to apply small-sample correction to var-cov matrix similar to RVE clubSandwich package used to obtain cluster-robust tests and CI

# running RE model using robust function 
as_metafor_result <- robust(as_metafor, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(as_metafor_result)

## obtain prediction interval -0.39, 0.20
print(predict(as_metafor_result))

## Equivalence Test: Anxiety Symptoms
TOSTmeta(ES=0.09, se=0.0372, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)

### sensitivity analysis on 5.3.2024 for comm's team
## effect of interventions on anxiety symtpoms for only those schools in public settings
## data subset d_anxiety_pubY


# create effect size id variable 'esid'
d_anxiety_pubY <- d_anxiety_pubY %>%
  group_by(refid) %>%
  mutate(esid = row_number())

# construct var-cov matrix assuming a correlation of 0.8 for effect sizes corresponding to the same study using vcalc function

as_V2 <- vcalc(via, cluster = refid,  obs=esid, data = d_anxiety_pubY, rho=0.8)

# Specify comparison model: metafor multilevel random-effects model with effect sizes nested within study 

# sigma is between study heterogeneity and within study heterogeneity
as_metafor_s1 <- rma.mv(yi, as_V2, random = ~1| refid/esid,  data = d_anxiety_pubY)
as_metafor_s1


## obtain prediction interval 
print(predict(as_metafor_s1))

# applying robust variance estimation
# data clustered by study
# adjust = TRUE to apply small-sample correction to var-cov matrix similar to RVE clubSandwich package used to obtain cluster-robust tests and CI

# running RE model using robust function 
as_metafor_result_s1 <- robust(as_metafor_s1, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(as_metafor_result_s1)

# TOST on finding (which is null, smd = -0.0016, se = 0.0368
TOSTmeta(ES=0.0016, se=0.0368, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)


```
### KQ1b: What is the effect of school-based anxiety prevention interventions on anxiety diagnoses?

#### Anxiety diagnoses

Meta-analysis results: 
 
```{r MA-anxiety-diagnosis, width = 10, tidy = TRUE}
# random-effect meta-analysis in metafor, no dependencies

# metafor random-effects model 

adx_metafor <- rma(yi, vi = via, data = d_adiagnosis, method = "REML")
adx_metafor

## obtain prediction interval (-0.25, 0.10)
print(predict(adx_metafor))

## transform to RR
predict(adx_metafor, transf = exp, digits = 2)

## Maria to add in equivalence test

# log risk ratio -0.4261
# log SE 0.2200
# from Sean, 0.85 to 1.17 for bounds (in risk ratio)
# when converting these to log values bounds are:-0.1625 and 0.1570
cilower <- log(0.85)
cilower
cihigher <- log(1.17)
cihigher
## Depression Symptoms Equivalence Test
TOSTmeta(ES=0.4261, se=0.2200, low_eqbound_d=-0.1625, high_eqbound_d=0.1570, alpha=0.05)


```


### KQ1c: What is the effect of school-based anxiety prevention interventions on depression symptoms?

#### Depression Symptoms

Meta-analysis results: 
  
```{r MA-depression-symptoms, width = 10, tidy = TRUE}


## Model 2 comparison model in metafor ################
# create effect size id variable 'esid'
d_depression <- d_depression %>%
  group_by(refid) %>%
  mutate(esid = row_number())

# construct var-cov matrix assuming a correlation of 0.8 # for effect sizes within the same study using vcalc
ds_V2 <- vcalc(via, cluster = refid,  obs=esid, data = d_depression, rho=0.8)

# metafor multilevel random-effects model 
# sigma is between study heterogeneity and within study heterogeneity (between variance is 0.00 and within is.01)
ds_metafor <- rma.mv(yi, ds_V2, random = ~1| refid/esid,  data = d_depression)
ds_metafor

## obtain prediction interval (-0.25, 0.10)
print(predict(ds_metafor))

# applying robust variance estimation
# data clustered by study
# adjust = TRUE to apply small-sample correction to var-cov matrix similar to RVE clubSandwich package used to obtain cluster-robust tests and CI

# running multivariate RE model using robust function 
ds_metafor_result <- robust(ds_metafor, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(ds_metafor_result)

## obtain prediction interval (-1.42, 1.39)
print(predict(ds_metafor_result))


## Depression Symptoms Equivalence Test
TOSTmeta(ES=0.07, se=0.0257, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)

```

#### Additional outcomes


### KQ1d: What is the effect of school-based anxiety prevention interventions on student well-being?

#### Well-being

Meta-analysis results: 
 
```{r MA-well-being, width = 10, tidy = TRUE}
# random-effect meta-analysis in metafor, no dependencies

# metafor random-effects model 

wb_metafor <- rma(yi, vi= via, data = d_wellbeing, method = "REML")
wb_metafor

## obtain prediction interval (-0.25, 0.10)
print(predict(wb_metafor))

## Well-Being Equivalence Test
TOSTmeta(ES=0.06, se=0.0626, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)



```
<!-- NOTES NEED UPDATING We did not run meta-analyses for the following outcomes due to low degrees of freedom or heterogeneity in outcomes (i.e.,
educational achievement:  -->

<!-- -   Educational Achievement (k = 3) -->
<!-- -   Self-Harm (k = 0) -->
<!-- -   Stress (k = 0)  -->
<!-- -   Substance Use (k = 0) -->
<!-- -   Suicidal Ideation (k = 1) -->


### KQ2: Do effects on anxiety symptoms vary by methodological, demographic, and intervention characteristics?

Meta-regression results examining heterogeneity in effect estimates for  anxiety and depression symptoms

NOTE: if code commented out, there is no variability in the moderator and model cannot be run (e.g., all trials with the depression symptom outcomes are RCTs)

NOTE: code for depression symtpoms included but not reported on in ETS presentation

```{r MA-meta-regressions, width = 10, tidy = TRUE}


## Moderator 1: Type of Assignment to Interventions 

# model 2 with metafor 
## first compute var-cov matrix
## this is the same var-cov as used in the main effect models but presenting again for clarity
V1_mr_d <- vcalc(via, cluster = refid,  obs=esid, data = d_depression, rho=0.8)
V1_mr_a <- vcalc(via, cluster = refid,  obs=esid, data = d_anxiety, rho=0.8)


# multivariate meta-regression (Working model)
rct_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ RCT_m, random = ~1| refid/esid,  data = d_anxiety)
rct_metaregression_a_mf

# apply robust function (final model) 
rct_metaregression_a_mf_adj <- robust(rct_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(rct_metaregression_a_mf_adj)


## Moderator 2: School Level Moderation
# depression

## metaregression with metafor (working model)

sl_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ secondary_m, random = ~1| refid/esid,  data = d_depression)
sl_metaregression_d_mf

# apply robust function (final model) 
sl_metaregression_d_mf_adj <- robust(sl_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(sl_metaregression_d_mf_adj)

# anxiety

##  metaregression with metafor (working model)

sl_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ secondary_m, random = ~1| refid/esid,  data = d_anxiety)
sl_metaregression_a_mf

# apply robust function (final model) 
sl_metaregression_a_mf_adj <- robust(sl_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(sl_metaregression_a_mf_adj)

## Moderator 3: School Type
# depression

## metaregression with metafor (working model)

public_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ public_m, random = ~1| refid/esid,  data = d_depression)
public_metaregression_d_mf

# apply robust function (final model) 
public_metaregression_d_mf_adj <- robust(public_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(public_metaregression_d_mf_adj)

# anxiety

## metaregression with metafor (working model)

public_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ public_m-1, random = ~1| refid/esid,  data = d_anxiety)
public_metaregression_a_mf

## Equivalence Test: Anxiety Symptoms and public_yes 
TOSTmeta(ES=0.0056, se=0.0402, low_eqbound_d=-0.1, high_eqbound_d=0.1, alpha=0.05)


# apply robust function (final model) 
public_metaregression_a_adj <- robust(public_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(public_metaregression_a_adj)


## school moderator
## add in new school moderator per comms team with levels: public, private, mixed, parochial, and cannottell
# factorize the moderator since it now has 5 levels
d_anxiety$school_mod <- factor(d_anxiety$school_mod)


## metaregression with metafor (working model)

school_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ school_mod, random = ~1| refid/esid,  data = d_anxiety)
school_metaregression_a_mf




# apply robust function (final model) 
school_metaregression_a_adj <- robust(school_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(school_metaregression_a_adj)
  

## Moderator 4: Country
# depression
## metaregression with metafor (working model)

country_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ Aust_m, random = ~1| refid/esid,  data = d_depression)
country_metaregression_d_mf

# apply robust function (final model) 
country_metaregression_d_adj <- robust(country_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(country_metaregression_d_adj)

# anxiety 

## metaregression with metafor (working model)

country_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ Aust_m, random = ~1| refid/esid,  data = d_anxiety)
country_metaregression_a_mf

# apply robust function (final model) 
country_metaregression_a_adj <- robust(country_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(country_metaregression_a_adj)

## Moderator 5: Level of Prevention
# depression 

## metaregression with metafor (working model)

prev_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ universal_m, random = ~1| refid/esid,  data = d_depression)
prev_metaregression_d_mf

# apply robust function (final model) 
prev_metaregression_d_adj <- robust(prev_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(prev_metaregression_d_adj)


# anxiety 

## metaregression with metafor (working model)

prev_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ universal_m, random = ~1| refid/esid,  data = d_anxiety)
prev_metaregression_a_mf

# apply robust function (final model) 
prev_metaregression_a_adj <- robust(prev_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(prev_metaregression_a_adj)

## Moderator 6: Comparator Type
# depression

## metaregression with metafor (working model)

comparator_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ TAU_m, random = ~1| refid/esid,  data = d_depression)
comparator_metaregression_d_mf

# apply robust function (final model) 
comparator_metaregression_d_mf_adj <- robust(comparator_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(comparator_metaregression_d_mf_adj)

# anxiety


## metaregression with metafor (working model)

comparator_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ TAU_m, random = ~1| refid/esid,  data = d_anxiety)
comparator_metaregression_a_mf

# apply robust function (final model) 
comparator_metaregression_a_mf_adj <- robust(comparator_metaregression_a_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(comparator_metaregression_a_mf_adj)

## Moderator 7: Years since publication
# depression


##  metaregression with metafor (working model)

year_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ year_m, random = ~1| refid/esid,  data = d_depression)
year_metaregression_d_mf

# apply robust function (final model) 
year_metaregression_d_mf_adj <- robust(year_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(year_metaregression_d_mf_adj)

# anxiety

## metaregression with metafor (working model)

year_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ year_m, random = ~1| refid/esid,  data = d_anxiety)
year_metaregression_a_mf

# apply robust function (final model) 
year_metaregression_a_mf_adj <- robust(year_metaregression_a_mf , cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(year_metaregression_a_mf_adj)

## Moderator 8: percent female
# depression

## metaregression with metafor (working model)

female_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ female_m, random = ~1| refid/esid,  data = d_depression)
female_metaregression_d_mf

# apply robust function (final model) 
female_metaregression_d_mf_adj <- robust(female_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(female_metaregression_d_mf_adj)

# anxiety

## metaregression with metafor (working model)

female_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ female_m, random = ~1| refid/esid,  data = d_anxiety)
female_metaregression_a_mf

# apply robust function (final model) 
female_metaregression_a_mf_adj <- robust(female_metaregression_a_mf , cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(female_metaregression_a_mf_adj)

## Moderator 9: too few studies report percent white to examine that moderator, which isn't ideal anyway. This is largely due to the majority of studies being conducted internationally

## Moderator 10: High RoB

# depression

## metaregression with metafor (working model)

rob_metaregression_d_mf <- rma.mv(yi, V1_mr_d, mods = ~ rob_high_m, random = ~1| refid/esid,  data = d_depression)
rob_metaregression_d_mf

# apply robust function (final model) 
rob_metaregression_d_mf_adj <- robust(female_metaregression_d_mf, cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(rob_metaregression_d_mf_adj)

# anxiety

## metaregression with metafor (working model)

rob_metaregression_a_mf <- rma.mv(yi, V1_mr_a, mods = ~ rob_high_m, random = ~1| refid/esid,  data = d_anxiety)
rob_metaregression_a_mf

# apply robust function (final model) 
rob_metaregression_a_mf_adj <- robust(rob_metaregression_a_mf , cluster = refid, adjust = TRUE, clubSandwich = TRUE)
summary(rob_metaregression_a_mf_adj)

## Comm's request to re-code moderator


```
